Probabilities and propensities: conversion experiences in online grocery shopping

### 2017-03-25 lists_conversion_experience.rmd
fixing humby reference to image
trying gh pages for paper

## Lists and orders

@@

## Conversion events: DunnHumby's work for Tesco

@@

## How the shopping list was reconstituted in the 1990s

@@

![Humby, 1984]( figure/2_humby_young_org_1994.png)

@@

## Reconfiguring recommendations

@@

## Ordering relevance through personhood or thinghood?

@@

## Sparsity: output 20 recommendations from 200,000 products

@@

## Experimental settings: A/B allocation and uplift

@@

## Infrastructure: the realtime engine serves

@@

## Similarity, substitution, complementarity and micrological propensities

>>>>

# Lists and orders

@@

# Conversion events: DunnHumby's work for Tesco

@@

# How the shopping list was reconstituted in the 1990s

@@

```{r humby-1984, fig.cap = 'Abstract from a Clive Humby presentation (Humby,1984)'}
include_graphics('figure/2_humby_young_org_1994.png')
```

@@

# Reconfiguring recommendations

@@

# Ordering relevance through personhood or thinghood?

@@

# Sparsity: output 20 recommendations from 200,000 products

@@

# Experimental settings: A/B allocation and uplift

@@

# Infrastructure: the realtime engine serves

@@

# Similarity, substitution, complementarity and micrological propensities
